Response to reviewers article 4780

### 2023-06-03 review/B-response.Rmd
update response

**\textcolor{purple}{Re: The comparison with other existing spatio-temporal class, i.e. stars and sftime, has been addressed in subsection 2.5 (after combining the original section 2 and 3 into section 2)}**

>>>>

**\textcolor{purple}{Re: The comparison with other existing spatio-temporal class, i.e. stars and sftime, has been addressed in Section 2.5 (after combining the original section 2 and 3 into section 2)}.**

  * **\textcolor{purple}{The stars object uses an array structure underneath while cubble is built from a tibble. It is a matter of choice from the analysts on which structure they are more comfortable to use. We believe spatio-temporal analysts who are more comfortable processing data with data frame (tidyverse) will benefit from cubble}**

  * **\textcolor{purple}{With sftime, the main benefit cubble provides is memory efficiency and this efficiency comes with the assumption that the spatial sites are fixed in cubble (full space-time grids and sparse space-time layouts). This is beneficial when spatial variables are duplicated because of long temporal observational frequency: daily or subdaily or when the spatial geoemtry (polygons or multipolygons) are expensive to duplicate. We include a quick comparison of object size between an sftime object and the same data in a cubble object in the paper.}**
